2_selection_variable

### 2019-12-16 r/2_selection_variable.Rmd
test
traitement (initialisation du rmd) + structure répertoire sur .md

```{r}
rf_selection = ranger(target ~ .,
                      data = data_imp %>% filter(dataset == "train") %>% select(-dataset, -id),
                      num.trees = 500,
                      importance = "impurity")

@@

>>>>

```{r}
set.seed(1156)
rf_selection = ranger(target ~ .,
                      data = data_imp %>% filter(dataset == "train") %>% select(-dataset, -id),
                      num.trees = 500,
                      importance = "impurity")

@@

## Exportation

On exporte la base avec les variables retenues.

```{r}
type_col = sapply(data_sel, class)

saveRDS(object = type_col,
      file = "./../data/data_sel_type_col.rds")
write.csv(x = data_sel,
          file = "./../data/data_sel.csv",
          quote = T,
          row.names = F)
```
